---
title: "All about Ada"
output: xaringan::moon_reader
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
library(tidyverse) # load tidyverse package
library(WikipediaR) # load WikipediaR package
library(lubridate) # load lubridate package
```

<!-- don't delete anything above me! -->

```{r eval = FALSE, include = FALSE}
# run this chunk to install packages
# once done, you can delete this chunk
# or you may wish to leave it with eval = FALSE
install.packages(tidyverse) # install tidyverse
install.packages(WikipediaR) # install WikipediaR
install.packages(lubridate) # install lubridate
```

# Overview

You'll use this document to build a `xaringan` slide deck and render to HTML using the xaringan `r fa(name = "r-project", fill = "#61acf0")` package, within a `blogdown` site.

You'll use this deck to tell us all about Ada Lovelace. The chunk of R code above called setup is very important- please do not delete that or the YAML header above it either.

Since this will be HTML, comments like this [<!--this is a comment-->] won't render in your final output.

# Ada data

```{r}
ada_contribs <- contribs(page = "Ada_Lovelace", rvprop = "user|userid|timestamp|size") %>% 
  pluck(2) %>% 
  as_tibble() %>% 
  mutate(size = as.double(size),
         timestamp = ymd_hms(timestamp)) %>% 
  filter(size > 0) 
```

# Who are these people?

```{r}
glimpse(ada_contribs)
```

```{r}
ggplot(ada_contribs, aes(x = timestamp, y = size)) +
  geom_line()
```

# Number of contributors

```{r eval = FALSE}
ada_contribs %>% 
  count(userid) %>% 
  ggplot(aes(x = timestamp, y = n)) + 
  geom_line()
```

